---
title: "Intro to Maps pt 2"
author: "Kristen Howard"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Load in Packages

```{r}
library(ggmap)
library(ggsn)
library(tidyverse)
library(here)
library(emojifont)
```

#### Here is how you register your API code. If the write function doesn't work. You will have to load this every single time. *NEVER* Push this info out into GitHub. This is confidential information tied to your credit card... no bueno.

```{r}
register_google(key = "YOUR KEY HERE", write = TRUE)
```

#### Load in Data

```{r}
ChemData <- read_csv(here("Week_07","Data","chemical_manualua.csv"))
```

```{r}
Oahu <- get_map("Oahu") #This is 
```

####You can now tuse ggmap to plot the base layer.

```{r}
ggmap(Oahu)
```

#You can specify certain coordinates if you are interested in that.

```{r}
WP <- data.frame(lon= -157.7621, lat= 21.27427)
Map1 <- get_map(WP)
ggmap(Map1) #To see the map, you have to use the ggmap function. If you don't you will see numbers. 
```

You can zoom in on a location, the larger the number, the more zoomed in it will be the range is 3 to 20

```{r}
Map1 <- get_map(WP,zoom = 17)
ggmap(Map1 )
```

You can also change the map type. The maptype can also be "watercolor". Go ahead and try it!

```{r}
Map1 <- get_map(WP,zoom = 17, maptype = "satellite")
```

#The ggmap base can be used as a base layer. Let's add points.

```{r}
ggmap(Map1)+
  geom_point(data = ChemData,
             aes(x = Long,
                 y = Lat,
                 color = Salinity),
                 size = 4) +
  scale_color_viridis_c()
```

```{r}
ggmap(Map1)+ #Rember to use ggmap
  geom_point(data = ChemData, 
             aes(x = Long, y = Lat, color = Salinity), 
             size = 4) + 
  scale_color_viridis_c()+
  scalebar( x.min = -157.766, x.max = -157.758,
           y.min = 21.2715, y.max = 21.2785,
            dist = 250, dist_unit = "m", model = "WGS84", #The model is specefic to your long/lat data. 
            transform = TRUE, st.color = "white",
            box.fill = c("yellow", "white"))
```

# How do you get the Lat and Long Data if you don't have it?

You can use geocode() function

```{r}
geocode("the white house")
```

you

```{r}
geocode("California State University, Northridge")
```

```{r}
geocode("Insert your own")
```

s

```{r}
library(emojifont)
search_emoji('smile')
```

```{r}
ggplot() + 
  geom_emoji('smile_cat',
             x = 1:5,
             y = 1:5,
             size = 10)
```
