---
title: "Cat_Spatial_Data_Analysis"
author: "Kristen Howard"
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    theme: caymen
    
---

# Introduction

Today, we will be using previous TidyTuesday data to practice using mapping functions associated with RStudio.Our objectives are:

1. Learn several mapping functions
2. Use TidyTuesday datset to create a **BEAUTIFUL** graph


# Load Packages
```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.path = "../Output/",
	message = FALSE,
	warning = FALSE
)
```


```{r}
library(here)
library(tidyverse)
library(tidytuesdayR)
library(ggplot2)
library(maps)
library(mapdata)
library(mapproj)
library(prettydoc)
```

# Load Data

```{r}
cats_uk <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-01-31/cats_uk.csv')
head(cats_uk)

```
-
# Create Map of United Kingdom
```{r Map_of_UK}

 UK <-map_data(map = "world", region = "UK")  #Let's create a map of the UK

UK %>%
  ggplot( aes(x = long,  # Select your df and specify the x and y values
                      y = lat, 
                      group = group)) + # This is very important when working with spatial data
  
 geom_polygon() +
 coord_map()
```

# Select Specefic Cat IDs 
We will chose Athena, Moscow, and Lola
```{r}
Tag_cat <- cats_uk%>%
              filter(tag_id %in% c("Athena","Moscow-Tag","Millie-Tag","Bobs-Tag"))
```

# Now, let's add data points from UK data.
```{r UK_Cat_Plot2}
ggplot() +
  geom_polygon(data=UK, #select the UK map we created earlier.
               aes(x=long,
                   y=lat,
                   group=group,
                   fill=region),
               color="#003300", 
               fill="#008000") +
  theme_minimal() + #This gets rid of grid and x and y axis.
  geom_point(data=Tag_cat, #This is how you add the points from another dataset and add it to a map
             aes(x = location_long, 
                 y = location_lat,
                 color= tag_id,
                 legend= tag_id)) +
  labs(title = "Map of Cat Locations in the United Kingdom",color = "Cat ID") +
  coord_map()+
  guides(fill=FALSE)
```

