---
title: "Lab Assignment - Function Programming"
author: "Kristen Howard"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
	fig.path = "../Output/",
	message = FALSE,
	warning = FALSE
)
```

# Directions
Create 2 useful functions, one plot function and one non-plot function
Give at least two examples for each function (at least 4 examples total)

#### Load Libraries

```{r}
library(tidyverse)
library(ggplot2)
library(here)
library(palmerpenguins)
library(RColorBrewer)
```

# Function 1
We are going to create a function that converts feet to inches.
we will be using trees data and an airplane data.

Based on the data dictionary, 
girth = 	Tree diameter (rather than girth, actually) in inches,
height = is in feet
volume = volume of timber in cubic feet

```{r}
view(trees)
```

```{r}
Airplane_Cleaned <- read_csv(here("Week_09","Data","Airplane_Cleaned.csv"))
View(Airplane_Cleaned)

```

#### Feet to Inches Function
```{r}
Feet_to_inches <- function(height_feet) {  
  height_inches <- (height_feet * 12) # Apply conversion, 1 feet is equal to 12 inches
  return(height_inches)
} 
```

Now let's apply it to the datasets we have loaded up

### Example 1
```{r}
# Example 1
trees_inches <- trees %>% # select df
                 mutate(Feet_to_inches(Height)) # creates a column with the converted values from function
view(trees_inches)
```

### Example 2
```{r}
# Example 2
airplane_inches <- Airplane_Cleaned %>% # select df
                      mutate('Height(in)' = Feet_to_inches(Height)) # creates a column with the converted values from function
view(airplane_inches)
```

# Function 2
We will create a function for a boxplot while using ggplot
```{r}
# First find two similar datasets and then create a map function
# Next, we will create a function for a box plot and a variety of categories!
view(iris)
view(penguins)
```

#### Customized Boxplot Function
```{r}
myplot<-function(data, x, y,species){ 
          ggplot(data, aes(x = {{x}}, 
                           y = {{y}},
                           fill = {{species}}))+
          geom_boxplot()+ # Creates box plot
          scale_fill_brewer(palette = 'Pastel2') + # applies color
          labs(x = "Species", # Label x-axis on both plots
               legend.position = "none") +
          theme_classic()  + # Set specific theme
          theme(plot.background = element_rect(fill = "#ffffe0"), # Change background color
                plot.title = element_text(hjust = 0.5))  # Center title for both graphs
 }
```

### Example 3
```{r Penguins Boxplot}
myplot(data = penguins, x = species, y = body_mass_g, species = species)+ # Use function and apply variables of interest
labs(y = "Body Mass (g)", # Label y axis
     title = "Species and Body Mass (g)") # Label title
```

### Example 4
```{r Iris Boxplot}
myplot(data = iris, x = Species, y = Petal.Length, Species) + # Use function and apply variables of interest
labs(y = "Petal Length (cm)", # Label y-axis
     title = "Species and Petal Length (cm)") # Label title

```

