---
title: "Howard - Good/Bad Plot"
author: "Kristen Howard"
date: "`r Sys.Date()`"
output:
  html_document:
   toc: TRUE
   toc_float: TRUE
   theme: flatly
---

# Introduction

Today we will be using previous TidyTuesday data containing data regarding Cocktails. First, load up the packages. This data contains information on popular cocktails, different categories, and much more!

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.path = "../Output/",
	message = FALSE,
	warning = FALSE
)
```

# Load Packages

```{r}
library(here)
library(tidyverse)
library(lubridate)
library(dplyr)
library(imager)
library(jpeg)
library(magick)
library(ggpattern)
library(RColorBrewer)
```

### load the data

```{r}
cocktails <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-26/cocktails.csv')
glimpse(cocktails)
view(cocktails)

```

### Add an Image

Now, Let's create our Bad graph! We want to add in an image in our background, so let's load in that image.

```{r Bar Image}
img <- image_read("https://images.unsplash.com/photo-1597290282695-edc43d0e7129?ixlib=rb-4.0.3&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=875&q=80")
# This is how you add in image

img %>% # Scale the image to make it fill the screen 
  image_scale("200")

img %>% # Blur the image for a dramatic effect and put a white haze on it
  image_blur(5, 5) %>%
  image_colorize(opacity = 20, color = "white")

```

### Subset the data and create graph

```{r, Bad Plot, echo = TRUE}

cocktails_clean <- cocktails %>% #Subset data to the variables of interest
  select(drink, ingredient_number,category,drink_thumb) %>%
  filter(category == 'Beer',
         ingredient_number < 4)

view(cocktails_clean) # check subsetted data


cocktails_clean %>% 
  ggplot( aes(x = ingredient_number,
              y = drink)) +
  annotation_custom(grid::rasterGrob(img # This grid replaced the usual panel. 
                                     , width = unit(1, "npc")
                                     , height = unit(1, "npc"))) +
  geom_violin_pattern( fill = '#f28e13', color = 'white',
                       pattern = 'circle', pattern_density = 0.3) + 
  coord_flip() +
  labs(title = 'SHOTS! SHOTS! SHOTS!') +
  theme(titl = element_text(angle = -45, hjust = 0)) +
  theme(axis.text.x = element_text(colour = "#FF10F0")) +  
  theme(panel.background = element_rect(fill = 'img'))+
  theme_void()

```

This chart is **bad** because there is NO indication on what is being measured on the x and y axis. Additionally, there are some major aesthetic issues. While there is a [title](https://www.youtube.com/watch?v=yNju8Rgwtg8), it is not centered and not enough information is given. Now you can enjoy a nice tall glass of beer!


Now, let's look at the good chart

```{r Good Plot}

cocktails %>%
  ggplot( aes(x = category,
              y = ingredient_number,
              fill = category)) +
  geom_violin() +
  theme_bw() +
  scale_fill_brewer(palette = "PiYG") +
  ggtitle(label = "Drink Category and Ingredients") +
  labs( x = "Cocktail Category",
        y = "Number of Ingredients") +
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(angle = 35, size = 8),
        axis.text.x = element_text(angle = -20, vjust = -0.3, size = 7),
        axis.title.x = element_text(size=10),
        axis.title.y = element_text(size=10)) +
  coord_flip()

```

This chart is **good** because there are clean labels on the x and y axis. This chart has broken down the the categories seen in this data set and is comparing the number of ingredients seen in each category. There is a clear label that is centered and there are no distracting colors to take away from the graph.
