---
title: "Week_11_b_Assignment"
author: "Kristen Howard"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.path = "../Output")
```
Today we will be using the skills we learned from the Strings and Vector lectures. Goals:
 - Clean up some issues with the character data
 - Use what you learned today to reorder your factors (into an order that makes sense)
 - Make column headers better. . . use janitor
 - Make a plot where one of the axes is a factor
 
### Load Library

```{r}
library(tidyverse)
library(here)
library(janitor) # Used to tidy up data
library(tidytext) # Used to tidy up data
library()
```


### Load data
```{r}
intertidal_data <- read_csv(here("Week_11","Data","intertidaldata.csv"))
view(intertidal_data) 
```



### Here are some issues that we are seeing:
There is no consistency on some of these. For example, there is some "Low  .(two spaces) and "Mid 1".
```{r}
intertidal_data$Quadrat


```

### Let's tackle these down below using {stringr}

```{r}
intertidal_data$Quadrat <- str_replace(intertidal_data$Quadrat, "Low  \\.","Low") # This solved the "Low  ." issue

intertidal_data$Quadrat <- str_replace(intertidal_data$Quadrat, "Mid  1", "Mid") # This solved the mid 1 issue

view(intertidal_data)
```


```{r}
intertidal_counts<-intertidal_data %>% # Select data
                    select(Quadrat) %>% # There are duplicate tide levels now!
                    mutate(Quadrat = factor(Quadrat, levels=c("Low", "Mid", "High")))  %>% # Make the quadrat location a factor
                    count(Quadrat) # This will create an n column of counts

intertidal_counts # The quadrats are not factors (<fctr>)
                  # Let's look at the different locations of quadrat in low, mid, or high tide 
```
### Create palatte
```{r}

my_palette <- c("#ccece6", "#66c2a4", "#238b45") # Let's create a palette 
```


```{r, Tide Graph}
intertidal_counts %>% # Select data
            ggplot(aes(x= Quadrat,
                       y = n,
                       fill = Quadrat)) +
            geom_col() + # Graph type. . . geom_bar does not show the proper counts on the 7 axis
            theme_bw() + # Set theme
            scale_fill_manual(values = my_palette) + # Use the palatte you created
            labs (x = " Quadrat Location at Tide Level", # Label accordingly
                  y = "Number of Counts",
                  title = "The Number of Observations at Each Tide Level")
```


