---
title: "RMarkdown 3/2/23 Lab Assignment"
author: "Kristen Howard"
date: "`r Sys.Date()`"
output: 
  html_document:
   toc: TRUE
   toc_float: TRUE
   theme: flatly
---

# Introduction

Today, we will be practiving various techniques and functions we have learned in RMarkdown. In today's lesson, we will be using data from the [*Palmer Penguin Package*](https://allisonhorst.github.io/palmerpenguins/).

# Objectives

Today we will be covering the following objectives:

-   Create an RMarkdown file and save outputs/scripts to the create location.
-   Create a RMarkdown file with clear explanations and headings
-   Create a production quality figures, which includes a table **AND** a graph.

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.path = "../Output/",
	message = FALSE,
	warning = FALSE
)
```

# Load Libraries

Now, lets load the appropriate libraries needed for this assignment. This would include the dataset from the palmerpenguin package.

```{r}
library(here)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(palmerpenguins)
library(kableExtra)
library(beyonce)
library(prettydoc)
```

# Load in Data

Now, lets observe our data with the following functions. Take a look at the various variables and start thinging about how you can model this data.

```{r}
#Observe the data
View(penguins)  
head(penguins) # This creates a tibble where we can see the names of                    columns.
```

# Creating a Table

Now, we will learn how to create a table in R. There is a way on how to do this in R. There are also a varity of packages to help you create visuals with your tables. Here is additional information on those packages. However, today we will be creating a package with Kable. Let's create a table looking at the average body mass of birds amoung the islands.

```{r PenguinBodyMass, fig.path="../Output/", include=FALSE}
penguins %>% #Select data
  select(body_mass_g, Island = island) %>%
    group_by(Island) %>% #Group by island
   summarise("Avgerage Body Mass" = mean(body_mass_g,na.rm = TRUE)) %>% #Calculates the mean 
    kbl(caption = "Average Body Mass per Island", position="center")%>% # make it a kable table 
    kable_classic() %>%
    column_spec(2, bold = T) %>% #This is how you chose the colors of rows
    row_spec(1, bold = T, color = "white", background = "hotpink") %>%
    kable_styling(full_width = FALSE) 
```

# Creating a Plot

Now, let's try to create a plot looking at the body mass, flipper length among species and sex.

```{r penguingraph}
penguins %>% #Select the data set
  ggplot(mapping = aes(x = body_mass_g, # Select your x and y variables
                       y = flipper_length_mm,
                       color = species, # Each point will be colored by species
                       shape = sex))  + # Each point will be shaped by sex
  geom_point()+ #This creates the points
  labs(x = "Body Mass (g)", #Label lets you name the x & y axis and legends. 
       y = "Flipper Length (mm)",
       color = "Species",
       shape = "Sex") +
 ggtitle(label = "Flipper Length and Body Mass Differences among Islands and Sex") +
 theme_bw() + #This is the theme that we have chose.
 scale_color_manual(values = beyonce_palette(11))

```
